### 2022-03-08 manuscript.tex
Update 02.tubaseq.md [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/6b74dd289e23ad30efba1d526e6f171f6bade1ce.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/6b74dd289e23ad30efba1d526e6f171f6bade1ce/checks
https://github.com/scherzerthesis/thesis/actions/runs/1953521573

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/979aac6c91cdcd60c73bd3dfdcd768979d6a1696/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/979aac6c91cdcd60c73bd3dfdcd768979d6a1696}{scherzerthesis/thesis@979aac6}
on March 8, 2022.

@@

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba2.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba4.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/6b74dd289e23ad30efba1d526e6f171f6bade1ce/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/6b74dd289e23ad30efba1d526e6f171f6bade1ce}{scherzerthesis/thesis@6b74dd2}
on March 8, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:05}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba2.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:05}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:07}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba4.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:07}
}
\end{figure}

\begin{figure}
\hypertarget{fig:08}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba5.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:08}
}
\end{figure}

\begin{figure}
\hypertarget{fig:09}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba6.svg}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:09}
}
\end{figure}
